Layered Formal Verification of a TCP Stack

### 2021-06-11 SecDev21/paper.tex
change back

Networking communication models define the processes of transferring information from one network component to another. Currently, the two most popular networking communication models are the TCP/IP (Transmission Control Protocol/Internet Protocol) \cite{TCP_IP:ietf_tutorial} and the OSI (Open System Interconnection) \cite{ISO:35.100} models. Layering is an essential design requirement for both models to achieve modularity, flexibility, and abstraction. Applications that only need to use the lower levels' functionality can ignore all the unnecessary upper levels. \Cref{Fig:TcpStack} shows the various layers of the OSI model. Each layer supports a wide range of protocols that are compatible with the layer's specifications. The lowest layers, bottom layers in \Cref{Fig:TcpStack}, are more hardware-oriented, while the top layers are more software-specific. While the \emph{application} level has a wide range of protocols that can be used depending on the application specification, the \emph{transport} layer is heavily dependent on the two dominant protocols: Transmission Control Protocol (TCP) and User Datagram Protocol (UDP). Today, almost every networking application, including IoT devices, is using either the TCP or the UDP protocols to traffic data between the Network and the Session layers. %Thus, the reliability, assurance, and security of these protocols are of paramount importance for critical applications.

>>>>

Networking communication models define the processes of transferring information from one network component to another. Currently, the two most popular networking communication models are the TCP/IP (Transmission Control Protocol/Internet Protocol) \cite{TCP_IP:ietf_tutorial} and the OSI (Open System Interconnection) \cite{ISO:35.100} models. Layering is an essential design requirement for both models to achieve modularity, flexibility, and abstraction. Applications that only need to use the lower levels' functionality can ignore all the unnecessary upper levels. \Cref{Fig:TcpStack} shows the various layers of the OSI model. Each layer supports a wide range of protocols that are compatible with the layer's specifications. The lowest layers, bottom layers in \Cref{Fig:TcpStack}, are more hardware-oriented, while the top layers are more software-specific. While the \emph{application} level has a wide range of protocols that can be used depending on the application specification, the \emph{transport} layer is heavily dependent on the two dominant protocols: Transmission Control Protocol (TCP) and User Datagram Protocol (UDP). Today, almost every networking application, including IoT devices, is using either the TCP or the UDP protocols to traffic data between the Network and the Application layers. %Thus, the reliability, assurance, and security of these protocols are of paramount importance for critical applications.
